Categories of Optics

### 2018-05-14 paper.tex
check inverses in Setter

\todo{Past work:
\begin{itemize}
\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
\item The Doubles paper
\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
\end{itemize}
}

\todo{Contributions:
\begin{itemize}
\item ...
\end{itemize}
}

\todo{Introduction should include:
\begin{itemize}
\item Previous attempts to generalise optics
\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
\end{itemize}
}
A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
\begin{itemize}
\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be \todo{represented faithfully in $S$},
\item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
\item ``$\fput\fput$'': $\fput (\fput \times \id_A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
\end{itemize}

@@

The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$: 
\begin{center}
\input{diagrams/identity-optic-full.tikz}
\end{center}
This dashed line above the diagram represents the unit object. As is standard, we will elide the unit object and unitors in future diagrams unless they are necessary. The diagram for the identity becomes simply:
\begin{center}
\input{diagrams/identity-optic.tikz}
\end{center}

@@

For the unit laws, suppose we have $\langle l, r \rangle : (S, S') \hto (A, A')$ with representative $M$. We calculate:
\begin{align*}
\id_{A, A'} \circ \langle l, r\rangle 
&= \langle \lambda^{-1}_A, \lambda_{A'} \rangle \circ \langle l, r\rangle \\
&= \langle (M \otimes \lambda^{-1}_A) l, r (M\otimes  \lambda_{A'})\rangle \\
&= \langle (\lambda^{-1}_M \otimes  A) l, r (\lambda_M \otimes A')\rangle \\
&= \langle l, r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')\rangle \\
&= \langle l, r \rangle  \\
\langle l, r \rangle \circ \id_{S, S'} 
&= \langle l, r \rangle \circ \langle \lambda^{-1}_S, \lambda_{S'}\rangle  \\
&= \langle (I \otimes l)\lambda^{-1}_S, \lambda_{S'} (I \otimes r) \rangle \\
&= \langle (\lambda^{-1}_M \otimes S)l, r (\lambda_{M} \otimes S') \rangle \\
&= \langle l, r (\lambda_{M} \otimes S')(\lambda^{-1}_M \otimes S') \rangle \\
&= \langle l, r \rangle
\end{align*}
Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend. 
\end{proof}

@@

\begin{proposition}
\label{prop-optic-functor}
Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\]
\end{proposition}
\begin{proof}
\todo{todo}
\end{proof}

@@

We must show that this is well defined. Suppose we have two lenses related by the coend relation:
\begin{align*}
\langle (f \otimes A) l, r \rangle = \langle l, r (f \otimes A') \rangle
\end{align*}
Then: \todo{do as string diagram}
\begin{align*}
K\langle (f \otimes A) l, r \rangle 
&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
%&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes (\varepsilon_{FN} (FN \otimes (Ff)^*)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}(A' \otimes f)))^* ) \\
&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
&= K\langle  l, r (f \otimes A') \rangle 
\end{align*}
\todo{functoriality} \todo{monoidal} \todo{preserves dualisable morphisms} \todo{preserves counit}
\end{proof}

\begin{remark}
It is unclear whether an argument like this can work in the case $\C$ is \emph{not} strict. There are a number of issues:

\begin{itemize}
\item Given $f : S \to A$ and $g : A' \to S'$, the optic $j(f) \otimes j(g)^* : (S \otimes I, I \otimes S') \hto (A \otimes I, I \otimes A')$ is not equal to $\iota(f, g)$. It is also not in a form that can be composed with the unitors of $\Optic_\C$, as the $I$s are not on the same side in either the domain or codomain.
\item \todo{wasn't there more?}
\end{itemize}

One possible workaround: We could extend the category of optics so it contains the image of $\C$ and its duals directly, without needing ghost morphisms $I \to I$ to face the other direction. So there are also objects $(S)$, and a morphism $(S) \hto (A)$ is either an $f : S \to A$ or the formal dual of a $g : A \to S$, and a morphism $(S) \hto (A, A')$ is an optic $(S, I) \hto (A, A')$.

There are several cases involved when composing morphisms and tensoring objects, depending on which kinds of objects are involved. This is significantly fiddlier, but it should allow a version of Proposition \ref{prop-optic-decompose} to apply to any $\C$.
\end{remark}

@@

@@

%\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
\begin{definition}[\cite{StrongFunctors}]
Suppose $(\C, \otimes, I)$ is a monoidal category. A \emph{(left) strength} for an endofunctor $F : \C \to \C$ is a natural transformation
\begin{align*}
\theta_{A,B} : A \otimes F B \to F(A \otimes B)
\end{align*}
such that both
\[
\begin{tikzcd}
1 \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
F A \ar[r, equals] & F A
\end{tikzcd}
\]
and
\[
\begin{tikzcd}
(A \otimes B) \otimes F C \ar[rr, "\theta_{A \otimes B, C}"] \ar[d, "\alpha_{A,B,FC}" left]  && F((A \otimes B) \otimes C) \ar[d, "F\alpha_{A,B,FC}" right] \\
A \otimes (B \otimes F C) \ar[r, "A \otimes \theta_{B,C}" below] & A \otimes F(B \otimes C) \ar[r, "\theta_{A, B\otimes C}" below] & F(A \otimes (B \otimes C))
\end{tikzcd}
\]
commute. A \emph{strong functor} is a functor equipped with a strength. A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
\[
\begin{tikzcd}
A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
\end{tikzcd}
\]

@@

In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref}

\begin{example}
An example, which we will use immediately, is the functor $FX = C \times \homC(D, X)$ in any cartesian closed category $\C$, and with any pair of objects $C$ and $D$. The strength is given by:
\begin{align*}
A \times FB = A \times C \times \homC(D, B) &\to C \times \homC(D, A \times B) = F(A \times B)\\
(a, c, f) &\mapsto (c, \lambda d. (a, fd))
\end{align*}
\end{example}

@@

\begin{lemma}
Suppose $\C$ is cartesian closed and $F : \C \to \C$ is strong with respect to $\times$. Then for any objects $A, B \in \C$, \[\C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)\]
\end{lemma}
\begin{proof}
Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation with components
\begin{align*}
A \times \homC(B, C) &\to FC \\
(a, g) &\mapsto F(\lambda x. \lambda h. h x)\theta_{\homC(B, C), B}(fa, g)
\end{align*}
%\begin{align*}
%A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
%\end{align*}
where $\theta$ is the strength for $F$.
\todo{Check this is a strong natural transformation}

Conversely, given an $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define
\begin{align*}
A &\to FB \\
a &\mapsto \eta_B(a, \lambda b. b)
\end{align*}
%$\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.

\todo{out of date:}
Checking these are inverse:
\begin{align*}
\Phi(\Psi(\eta))_C &= \Phi(\eta_B(A\times\const_{\id_B}))_C \\
&= (F\epsilon) \theta_{\homC(B, C), B} \left( \eta_B(A\times\const_{\id_B}) \times \id_{\homC(B, C)} \right)
\end{align*}
\todo{todo, using the strength for $A \times \homC(B, -)$?}
\end{proof}

This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that were used.

Now, we can construct setters.

\begin{definition}
Supposed $\C$ is cartesian closed, and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of lawful optics for this action.
\end{definition}

Due to the above lemma, we can eliminate the coend from this definition:
\begin{align*}
\Setter_\C(S, A) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA, S) \\
&\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA, S) \\
&\cong \C(S \times \homC(A, A), S) \\
&\cong \C(\homC(A, A), \homC(S,S))
\end{align*}

@@

This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal---in other words---there are fewer affine traversals than expected.

@@

\begin{remark}
For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the corresponding functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
\end{remark}

\subsection{Traversals}
\todo{Do it}

\subsection{``Achromatic'' Lenses}

@@

\begin{definition}
There is a category $\Tamb_\C(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
\[
\begin{tikzcd}
P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
Q(A,B) \ar[r, "\beta_{A,B,M}"] & Q(MA, MB)
\end{tikzcd}
\]
commutes.
\end{definition}

This category is monoidal with respect to $\odot$ as given above, and the monoidal unit is given by $I$. There is an evident forgetful functor $U : \Tamb_\C(\M) \to \Prof(\C, \C)$ that is strong monoidal. This forgetful functor has both a left and right adjoint; particularly important for us is the left adjoint:

\begin{definition}
Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ be the functor \todo{change notation? drop $\C$ if we use the same one the whole time?}
\begin{align*}
\Pastro_\M(P) := \int^{M \in \M}  \C(-, M{=}) \odot P \odot \C(M-, {=}) 
\end{align*}
Or, in other words, 
\begin{align*}
\mathrm{Pastro}_\C(\M)(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
\end{align*}
The module structure $\alpha_{A,B,M} : \Pastro_\M(P)(A,B) \to \Pastro_\M(P)(MA, MB)
$ is given by map induced by 
\begin{align*}
&\int^{C,D \in \C} \C(A, NC) \times P(C,D) \times  \C(ND, B) \\
\xrightarrow{\text{functoriality}} \quad& \int^{C,D \in \C} \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
\xrightarrow{\copr_{MN}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(MA, NC) \times P(C,D) \times  \C(ND, MB) \\
= \quad&\Pastro_\M(P)(MA, MB)
\end{align*}
for all $N \in \M$.
\end{definition}

\begin{proposition}
$\Pastro_\M : \Prof(\C, \C) \to \Tamb_\C(\M)$ is left adjoint to $U : \Tamb_\C(\M) \to \Prof(\C, \C)$.
\end{proposition}
\begin{proof}
\todo{Could crunch through this manually, may be a neat way to do it using techniques from P/S}
\end{proof}

@@

\begin{proposition}
The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
\end{proposition}
\begin{proof}
\todo{Is there a point to proving this?}
\end{proof}

Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$. This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$.

\begin{lemma}
\label{lemma-rep}
The functor $(U-)(A,A) : \Tamb_\C(\M) \to \Set$ is representable: there is a natural isomorphism
$(U-)(A,A) \cong \Tamb_\C(\M)(\Pastro_\M E_A, -)$
\end{lemma}
\begin{proof}
We have the chain of natural isomorphisms:
\begin{align*}
&(U-)(A,A) \\
\cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda (un)reduction twice)} \\
=\;&\int_{X,Y \in \C} \Set(E_A(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
\cong \;&\Prof(E_A, U-) && \text{(natural transformations as ends)} \\
\cong \;&\Tamb_\C(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)} 
\end{align*}
\end{proof}

@@

\begin{proposition}
\label{prop-profunctor-optics-are-optics}
\begin{align*}
[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
\end{align*}
\end{proposition}
\begin{proof}
We have the chain of isomorphisms:
\begin{align*}
&[\Tamb_\C(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
\cong \;&[\Tamb_\C(\M), \Set](\Tamb_\C(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
\cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S) \\
= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A,D) \times \C(MD,S) \\
\cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
= \;&\Optic_\M(S, A)
\end{align*}
\todo{This works for $\Optic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}

@@

Therefore the functor $\Tamb_\C(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.

>>>>

%\todo{Past work:
%\begin{itemize}
%\item The Haskell lens people: edwardk, shachaf, xplat, roconnor... (TODO: find out who these people are)
%\item The Doubles paper
%\item Bartosz's blog post which was written about the same time I started this. (Only tensor-like optics, no discussion of laws, confusion about enrichment(?))
%\item The profunctor optics paper out of Oxford. (No generality, nothing categorical, no discussion of laws)
%\end{itemize}
%}
%
%\todo{Contributions:
%\begin{itemize}
%\item ...
%\end{itemize}
%}
%
%\todo{Introduction should include:
%\begin{itemize}
%\item Previous attempts to generalise optics
%\item Some remark about how it's hard to isolate exactly what $\Set$-like properties are being used
%\end{itemize}
%}
A lens from $S$ to $A$ is a pair of maps $\fget : S \to A$ and $\fput : S \times A \to S$ that typically obeys three laws (whose names are in diagrammatic order):
\begin{itemize}
\item ``$\fput\fget$'': $\fget \; \fput = \pi_2$ as maps $S \times A \to A$, so that any update to $A$ should be \todo{represented faithfully in $S$},
\item ``$\fget\fput$'': $\fput [\id_S, \fget] = \id_S$ as maps $S \to S$, so that if $A$ is not changed then $S$ should not change; and,
\item ``$\fput\fput$'': $\fput (\fput \times \id_A) = \fput \, \pi_{1, 3}$ as maps $S \times A \times A \to S$, so any update to $A$ completely overwrites previous updates.
\end{itemize}

@@

The identity optic $(S, S') \hto (S, S')$ is given by $\langle \lambda^{-1}_S, \lambda_{S'} \rangle$, where $\lambda_S : I \otimes S \to S$ is the left unitor for $S$: 
\begin{center}
\input{diagrams/identity-optic-full.tikz}
\end{center}
This dashed line above the diagram represents the unit object. As is standard, we will elide the unit object and unitors in future diagrams unless they are necessary. The diagram for the identity becomes:
\begin{center}
\input{diagrams/identity-optic.tikz}
\end{center}

@@

For the unit laws, suppose we have $\langle l, r \rangle : (S, S') \hto (A, A')$ with representative $M$. We calculate:
\begin{align*}
\id_{A, A'} \circ \langle l, r\rangle 
&= \langle \lambda^{-1}_A, \lambda_{A'} \rangle \circ \langle l, r\rangle \\
&= \langle (M \otimes \lambda^{-1}_A) l, r (M\otimes  \lambda_{A'})\rangle \\
&= \langle (\lambda^{-1}_M \otimes  A) l, r (\lambda_M \otimes A')\rangle \\
&= \langle l, r (\lambda_M \otimes A') (\lambda^{-1}_M \otimes A')\rangle \\
&= \langle l, r \rangle  \\
\langle l, r \rangle \circ \id_{S, S'} 
&= \langle l, r \rangle \circ \langle \lambda^{-1}_S, \lambda_{S'}\rangle  \\
&= \langle (I \otimes l)\lambda^{-1}_S, \lambda_{S'} (I \otimes r) \rangle \\
&= \langle (\lambda^{-1}_M \otimes S)l, r (\lambda_{M} \otimes S') \rangle \\
&= \langle l, r (\lambda_{M} \otimes S')(\lambda^{-1}_M \otimes S') \rangle \\
&= \langle l, r \rangle
\end{align*}
Where in both cases we have used the naturality of $\lambda$ and coend relations to move $\lambda^{-1}_M$ to the right-hand side of the coend, where it may be cancelled.
\end{proof}

@@

\begin{proposition}
\label{prop-optic-functor}
Collectively this operation defines a \todo{pseudo?}functor \[\Optic : \SymmMonCat \to \SymmMonCat.\] \qed
\end{proposition}

@@

We must show that this is well defined. Suppose we have two lenses related by the coend relation:
\begin{align*}
\langle (f \otimes A) l, r \rangle = \langle l, r (f \otimes A') \rangle
\end{align*}
Then: \todo{maybe do as string diagram}
\begin{align*}
K\langle (f \otimes A) l, r \rangle 
&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F(s_{M,A}(f \otimes A)l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(F((A \otimes f)s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
%&= (FA \otimes \varepsilon_{FM} \otimes (FA')^*)(FA \otimes Ff \otimes FM \otimes FA')(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes (\varepsilon_{FM} (Ff \otimes FM)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes (\varepsilon_{FN} (FN \otimes (Ff)^*)) \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}))^* ) \\
&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(rs_{A',M}(A' \otimes f)))^* ) \\
&= (FA \otimes \varepsilon_{FN} \otimes (FA')^*)(F(s_{N,A}l) \otimes (F(r(f \otimes A')s_{A',N}))^* ) \\
&= K\langle  l, r (f \otimes A') \rangle 
\end{align*}
\todo{functoriality} \todo{monoidal} \todo{preserves dualisable morphisms} \todo{preserves counit}
\end{proof}

@@

\todo{As we get higher up in the hierarchy, the `ad-hoc' laws get closer to being the same as the coend laws}

@@

%\todo{Taken from http://cs.ioc.ee/~tarmo/ssgep15/ssgep-1a.pdf}
\begin{definition}[\cite{StrongFunctors}]
Suppose $(\C, \otimes, I)$ is a monoidal category.  A \emph{(left) strong functor} is a functor $F : \C \to \C$ equipped with a natural transformation
\begin{align*}
\theta_{A,B} : A \otimes F B \to F(A \otimes B)
\end{align*}
such that both
\[
\begin{tikzcd}
1 \otimes F A \ar[r, "\theta_{1,A}"] \ar[d, "\cong" left]  & F(1 \otimes A) \ar[d, "\cong" right] \\
F A \ar[r, equals] & F A
\end{tikzcd}
\]
and
\[
\begin{tikzcd}
(A \otimes B) \otimes F C \ar[rr, "\theta_{A \otimes B, C}"] \ar[d, "\alpha_{A,B,FC}" left]  && F((A \otimes B) \otimes C) \ar[d, "F\alpha_{A,B,FC}" right] \\
A \otimes (B \otimes F C) \ar[r, "A \otimes \theta_{B,C}" below] & A \otimes F(B \otimes C) \ar[r, "\theta_{A, B\otimes C}" below] & F(A \otimes (B \otimes C))
\end{tikzcd}
\]
commute. A \emph{strong natural transformation} $\tau : (F,\theta) \to (G,\theta')$ is a natural transformation that respects the strength:
\[
\begin{tikzcd}
A \otimes F B \ar[r, "\theta_{A,B}"] \ar[d, "A \otimes \tau_B" left]  & F(A \otimes B) \ar[d, "\tau_{A \otimes B}" right] \\
A \otimes G B \ar[r, "\theta'_{A, B}"]& G(A \otimes B)
\end{tikzcd}
\]

@@

In what follows, we will exploit the convenient $\lambda$-calculus syntax for morphisms in a cartesian closed category. \todo{ref} \todo{this sudden change in notation is a bit confusing}

\begin{example}
An example, which we will use immediately, is the functor $FX = A \times \homC(B, X)$ in any cartesian closed category $\C$, and with any pair of objects $A$ and $B$. The strength $s_{C,D}$ is given by:
\begin{align*}
C \times FD = C \times A \times \homC(B, D) &\to A \times \homC(B, C \times D) = F(C \times D)\\
(c, a, f) &\mapsto (a, \lambda d. (c, fd))
\end{align*}
\end{example}

@@

\begin{lemma}
Suppose $\C$ is cartesian closed and $F : \C \to \C$ is strong with respect to $\times$. Then for any objects $A, B \in \C$, \[\C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)\]
\end{lemma}
\begin{proof}
We construct the isomorphism $\Phi: C(A, FB) \cong \Strong_\C(\times)(A \times \homC(B, -), F)$ and its inverse $\Psi$.
Given a $f \in \C(A, FB)$, let $\Phi(f)$ be the natural transformation such that the component at $C$ is the composite 
\begin{align*}
A \times \homC(B, C) \to FB \times \homC(B, C) \to F(B \times \homC(B, C)) \to FC
\end{align*}
I.e.,
\begin{align*}
A \times \homC(B, C) &\to FC \\
(a, g) &\mapsto F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, f a))
\end{align*}
%\begin{align*}
%A \times \homC(B, C) \xrightarrow{f \times \id} FB \times \homC(B, C) \xrightarrow{\theta_{\homC(B, C), B}}  F(B \times \homC(B, C)) \xrightarrow{F\epsilon} FC
%\end{align*}
where $\theta$ is the strength for $F$.
\todo{Check this is a strong natural transformation}

Conversely, given a strong natural transformation $\eta : A \times \homC(B, -) \Rightarrow F$, the component at $B$ is a function $\eta_B : A \times \homC(B, B) \to FB$; we define $\Psi(\eta) : A \to FB$ by $\Psi(\eta)(a) = \eta_B(a, \id_B)$

%$\Psi(\eta) : A \to FB$ to be $A \xrightarrow{A \times \const_{\id_B}} A \times \homC(B, B) \xrightarrow{\eta_B} FB$.

Now, verifying these are inverse:
\begin{align*}
\Phi(\Psi(\eta))_C (a,g)
&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \Psi(\eta)(a))) \\
&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(g, \eta_B(a, \id_B))) \\
&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, C), B}(\id, \eta_B)(g, (a, \id_B))) \\
&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} s_{\homC(B, C), B}(g, a, \id_B)) && \text{($\theta$ is a strong transformation)}\\
&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, \id_B d)) ) && \text{(definition of $s$)}\\
&= F(\lambda x. \lambda h. h x)(\eta_{\homC(B, C) \times B} (a, \lambda d. (g, d)) ) \\
&= \eta_{C}(\lambda (a, f). (a, \lambda b. \mathsf{fst}(f b)\mathsf{snd}(f b)) (a, \lambda d. (g, d)) && \text{(naturality of $\eta$)}\\
&= \eta_{C}(a, \lambda b. g b) \\
&= \eta_{C}(a, g)
\end{align*}
And in the other direction:
\begin{align*}
\Psi(\Phi(f))(a) 
&= \Phi(f)_B(a, \id_B) \\
&= F(\lambda x. \lambda h. h x)(\theta_{\homC(B, B), B}(\id_B, f a))\\
&= F(\lambda x. \lambda h. h x)(F(\lambda b. (\id_B, b)))\theta_{1, B}(f a) && \text{(naturality of $\theta$)}\\
&= F(\lambda b. \id_B b)\theta_{1, B}(f a)\\
&= \theta_{1, B}(f a) && \text{(strength of $\theta$)}\\
&= f a
\end{align*}
\end{proof}

This is a generalisation of \cite[Proposition 2.2]{SecondOrderFunctionals}, isolating the properties of $\Set$ that are used. We can now construct setters:

\begin{definition}
Supposed $\C$ is cartesian closed and let $\Strong(\C)$ act on $\C$ by evaluation. The \emph{category of setters} $\Setter_\C$ is the category of optics for this action.
\end{definition}

Due to the above lemma, we can eliminate the coend from the definition:
\begin{align*}
\Setter_\C((S, S'), (A, A')) &= \int^{F \in \Strong(\C)} \C(S, FA) \times \C(FA', S') \\
&\cong \int^{F \in \Strong(\C)} \Strong_\C(\times)(S \times \homC(A, -), F)  \times \C(FA', S') \\
&\cong \C(S \times \homC(A, A'), S') \\
&\cong \C(\homC(A, A'), \homC(S,S'))
\end{align*}

@@

This set includes into $\C(S, A \sqcup S') \times \C(S\times A', S')$, but the two are not equal. In other words, there are fewer affine traversals than expected.

@@

\begin{remark}
For this argument to work, it is important that the morphisms in $\mathsf{Aff}$ are just those in $\C \times \C$, even though there are likely to be more natural transformations between the functors $P \sqcup (Q \times -)$ and $P' \sqcup (Q' \times -)$.
\end{remark}

\subsection{Traversals}
\todo{todo}

\subsection{``Achromatic'' Lenses}
\todo{http://oleg.fi/gists/posts/2018-03-28-achromatic-lens.html}

@@

\begin{definition}
There is a category $\Tamb(\M)$ of Tambara modules and natural transformations that respect the extra structure, in the sense that for any $l : P \to Q$, the diagram
\[
\begin{tikzcd}
P(A,B) \ar[r, "\alpha_{A,B,M}"] \ar[d, "l_{A,B}" left] & P(MA, MB) \ar[d, "l_{MA, MB}" right] \\
Q(A,B) \ar[r, "\beta_{A,B,M}"] & Q(MA, MB)
\end{tikzcd}
\]
commutes.
\end{definition}

This category is monoidal with respect to $\odot$ as given above, and the monoidal unit is given by $I$. There is an evident forgetful functor $U : \Tamb(\M) \to \Prof(\C, \C)$ that is strong monoidal. This forgetful functor has both a left and right adjoint; particularly important for us is the left adjoint:

\begin{definition}
Let $\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ be the functor:
\begin{align*}
\Pastro_\M(P) := \int^{M \in \M}  \C(-, M{=}) \odot P \odot \C(M-, {=}) 
\end{align*}
Or, in other words, 
\begin{align*}
\mathrm{Pastro}_\C(\M)(P)(A,B) := \int^{M \in \M} \int^{C,D \in \C} \C(A, MC) \times P(C,D) \times  \C(MD, B)
\end{align*}
The module structure $\alpha_{A,B,M} : \Pastro_\M(P)(A,B) \to \Pastro_\M(P)(MA, MB)
$ is given by map induced by 
\begin{align*}
&\int^{C,D \in \C} \C(A, NC) \times P(C,D) \times  \C(ND, B) \\
\xrightarrow{\text{functoriality}} \quad& \int^{C,D \in \C} \C(MA, MNC) \times P(C,D) \times  \C(MND, MB) \\
\xrightarrow{\copr_{MN}} \quad&\int^{N \in \M} \int^{C,D \in \C} \C(MA, NC) \times P(C,D) \times  \C(ND, MB) \\
= \quad&\Pastro_\M(P)(MA, MB)
\end{align*}
for all $N \in \M$.
\end{definition}

\begin{proposition}
$\Pastro_\M : \Prof(\C, \C) \to \Tamb(\M)$ is left adjoint to $U : \Tamb(\M) \to \Prof(\C, \C)$.
\end{proposition}
\begin{proof}
\todo{Could crunch through this manually, may be a neat way to do it using techniques from P/S}
\end{proof}

@@

%\begin{proposition}
%The category $\Optic_\M$ is isomorphic to the full subcategory on objects of the form $E_A$ in the Kleisli category for the monad $U \Pastro_\M : \Prof(\C, \C) \to \Prof(\C, \C)$.
%\end{proposition}
%\begin{proof}
%\todo{Is there a point to proving this?}
%\end{proof}

Given a profunctor, or indeed a Tambara module, we can evaluate it at any two objects of $\C$. This process is functorial in the choice of Tambara module, giving a functor $(U-)(A,A) : \Tamb(\M) \to \Set$.

\begin{lemma}
\label{lemma-rep}
The functor $(U-)(A,A) : \Tamb(\M) \to \Set$ is representable: there is a natural isomorphism
$(U-)(A,A) \cong \Tamb(\M)(\Pastro_\M E_A, -)$
\end{lemma}
\begin{proof}
We have the chain of natural isomorphisms:
\begin{align*}
&(U-)(A,A) \\
\cong \;&\int_{X,Y \in \C} \Set(\C(X,A) \times \C(A,Y), (U-)(X,Y)) && \text{(by Yoneda (un)reduction twice)} \\
=\;&\int_{X,Y \in \C} \Set(E_A(X,Y), (U-)(X,Y)) && \text{(by definition)}\\
\cong \;&\Prof(E_A, U-) && \text{(natural transformations as ends)} \\
\cong \;&\Tamb(\M)(\Pastro_\M E_A, -) && \text{(by adjointness)} 
\end{align*}
\end{proof}

@@

\begin{proposition}
\label{prop-profunctor-optics-are-optics}
\begin{align*}
[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) &\cong \Optic_\M(S, A)
\end{align*}
\end{proposition}
\begin{proof}
We have the chain of isomorphisms:
\begin{align*}
&[\Tamb(\M), \Set]((U-)(A,A),(U-)(S,S)) \\
\cong \;&[\Tamb(\M), \Set](\Tamb(\M)(\Pastro_\M E_A, -), (U-)(S,S))  && \text{(by Lemma \ref{lemma-rep})}\\
\cong \;&(U\Pastro_\M E_A)(S,S)  && \text{(by Yoneda)} \\
= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times E_A(C,D) \times \C(MD,S) \\
= \;&\int^{M \in \M} \int^{C,D \in \C} \C(S, MC) \times \C(C,A) \times \C(A,D) \times \C(MD,S) \\
\cong \;&\int^{M \in \M} \C(S, MA) \times \C(MA, S)  && \text{(by co-Yoneda twice)} \\
= \;&\Optic_\M(S, A)
\end{align*}
\todo{This works for $\Optic_\M((S, S'), (A, A'))$ just fine, just define $E_{A,A'}$ in the obvious way.}

@@

Therefore the functor $\Tamb(\M)(\Pastro_\M E_A, -)$ is canonically lax monoidal, and so the isomorphic functor $(U-)(A,A)$ is also.
